Star-galaxy Classification Using Deep Convolutional Neural Networks

### 2016-10-04 paper/main.tex
update paper

Using the CasJobs server, we randomly select a total of 65,000 sources,
which are either stars or galaxies.\footnote{
\changed{
We exclude objects that clearly are neither stars nor galaxies.
Most of the excluded objects are QSOs or quasars.
Quasars appear as point sources, rather than resolved sources similar to
galaxies,
and many of them have one or more saturated pixels in the images.
They are also different from galaxies because of their intrinsic variability on
a wide range of time scales, which may be due to variation in the accretion rate
or instabilities of the accretion disk around the black hole
\citep{popovic2012photocentric}.
However, unlike any known stars, their spectra show strong and broad emission
lines.
Thus, many studies exclude quasars in the binary star-galaxy classification
scheme
\citep[\eg][]{vasconcellos2011decision,Fadely2012}.
Expanding the historical star-galaxy classification problem to include
other classes may have advantanges~\citep{ball2006robust}, and we defer
the results of this multi-class problem to a future paper.}
}
We exclude some bad photometric observations as follows.
We consider only objects
with no warning flags in the spectroscopic measurement (\texttt{zWarning = 0});
the half-light radius in the $r$ band is less than 30 arc seconds
as measured by the exponential and de Vaucouleurs light profiles;
the error on the spectroscopic redshift measurement is less than 0.1; and
the spectroscopic redshift is less than 2.

>>>>

Using the CasJobs server, we randomly select a total of 65,000 sources,
which are either stars or galaxies.
\changed{
In this work, we exclude objects that clearly are neither stars nor galaxies.
Most of the excluded objects are QSOs or quasars.
Quasars appear as point sources, rather than resolved sources similar to
galaxies,
and many of them have one or more saturated pixels in the images.
However, unlike any known stars, their spectra show strong and broad emission
lines.
Quasars are also different from galaxies because of their intrinsic variability
on a wide range of time scales, which may be due to variation in the accretion
rate or instabilities of the accretion disk around the black hole
\citep{popovic2012photocentric}.
Thus, many studies exclude quasars in the binary star-galaxy classification
scheme~\citep[\eg][]{vasconcellos2011decision,Fadely2012}.
Expanding the historical star-galaxy classification problem to include
additional classes, \eg \textit{nsng} (neither star nor galaxy),
may have advantanges~\citep{ball2006robust}, and we plan to present
the results of this multi-class problem in a future paper.
}

We also exclude some bad photometric observations as follows.
We consider only objects
with no warning flags in the spectroscopic measurement (\texttt{zWarning = 0});
the half-light radius in the $r$ band is less than 30 arc seconds
as measured by the exponential and de Vaucouleurs light profiles;
the error on the spectroscopic redshift measurement is less than 0.1; and
the spectroscopic redshift is less than 2.
